---
title: "Assigment - Naive Bayes DIY"
author:
  - name author here - Caesar Bobson
  - name reviewer here - Joel van Bragt
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
   html_notebook:
    toc: true
    toc_depth: 2
---

```{r}
#install.packages("RColorBrewer")
#install.packages("magrittr")
#install.packages("base")
#install.packages("e1071")

library(wordcloud)
library(e1071)
library(RColorBrewer)
library(magrittr)
library(base)
library(readr)
library(utils)
library(tidyverse)
library(tm)
library(caret)
```

## 1) Business Understanding 
Creating a machine learning program that recognizes when an item is likely to be fake. Using the Fake News data set for Data Mining (Categorization).

Import Data
```{r}

url <- "https://raw.githubusercontent.com/HAN-M3DM-Data-Mining/assignments/master/datasets/NB-fakenews.csv"
rawDF <- read_csv(url)

head(rawDF)

```
```{r}
rawDF <- rawDF[c(-1,-3)] %>% na.omit
head(rawDF)
```
Factor conversion
```{r}
rawDF$label <- rawDF$label %>% factor %>% relevel("1")
class(rawDF$label)

rawDF$label <- rawDF$label %>% factor %>% relevel("0")
class(rawDF$label) 

Fake <- rawDF %>% filter(label == "1")
NFake <- rawDF %>% filter(label == "0")
```
Format Adjustments
```{r}
wordcloud(Fake$text, max.words = 20, scale = c(4, 0.8), colors= c("blue","blue2","blue3","blue4"))
wordcloud(NFake$text, max.words = 20, scale = c(4, 0.8), colors= c("indianred1","indianred2","indianred3","indianred4"))
```
## 2) Data Preparation
Corpus for Training data and it is necessary to construct a corpus -> collection of text documents

```{r}
rawCorpus <- Corpus(VectorSource(rawDF$title))
inspect(rawCorpus[1:3])

cleanCorpus <- rawCorpus %>% tm_map(tolower) %>% tm_map(removeNumbers)
cleanCorpus <- cleanCorpus %>% tm_map(tolower) %>% tm_map(removeWords, stopwords()) %>% tm_map(removePunctuation)
cleanCorpus <- cleanCorpus %>% tm_map(stripWhitespace)
```
Inspect data 
```{r}
tibble(Raw = rawCorpus$content[1:3], Clean = cleanCorpus$content[1:3])
```
```{r}
cleanDTM <- cleanCorpus %>% DocumentTermMatrix
inspect(cleanDTM)
```

```{r}
set.seed(1234)
trainIndex <- createDataPartition(rawDF$label, p = 0.75, 
                                  list = FALSE,
                                  times = 1)

head(trainIndex)
```
Train and test 

```{r}
trainDF <- rawDF[trainIndex, ]
testDF <- rawDF[-trainIndex, ]

trainCorpus <- cleanCorpus[trainIndex]
testCorpus <- cleanCorpus[-trainIndex]

trainDTM <- cleanDTM[trainIndex, ]
testDTM <- cleanDTM[-trainIndex, ]
```

I set an assumption that a word must appear 120 times in order to be included

```{r}
freqWords <- trainDTM %>% findFreqTerms(120)
trainDTM <-  DocumentTermMatrix(trainCorpus, list(dictionary = freqWords))
testDTM <-  DocumentTermMatrix(testCorpus, list(dictionary = freqWords))  
```
Here we need to convert the numerical matrix into a binary factor (true or false) by mapping a function for better classification and categorization.
```{r}
convert_counts <- function(x) {
  x <- ifelse(x > 0, 1, 0) %>% factor(levels = c(0,1), labels = c("No", "Yes"))
}

nColsDTM <- dim(trainDTM)[2]
trainDTM <- apply(trainDTM, MARGIN = 2, convert_counts)
testDTM <- apply(testDTM, MARGIN = 2, convert_counts)

head(trainDTM[,1:10]) 
```
## 3) Modeling
```{r}
nbayesModel <-  naiveBayes(trainDTM, trainDF$label, laplace = 1)
```
Confusion Matrix
Categorization of predictions against the actual Values
```{r}
predVec <- predict(nbayesModel, testDTM)
confusionMatrix(predVec, testDF$label, positive = "1", dnn = c("Prediction", "True"))
``` 
## 4) Evaluation and Deployment 
The model has an accuracy of approximately 90% which is relatively good, with Kappa coefficient (Cohen's Kapper)of 0,8 indicating a good agreement between classification and truth values. Also the Sensitivity or recall rate is quite high (97%) and so is Neg Pred Value (97%) which reflects the probability that a predicted negative is true negative. Overall -> good model


## Reviewers's evaluation and suggestion
As of now, I have seen no mistakes by the author. However, maybe the criteria for the frequency is a bit high (120), and the author can adjust it to under 100 frequency.
Overall, neat work!
